NewAnalysis

### 2024-11-12 Code/NewAnalysis.Rmd
Added random effect graphs

Here is the qq plot for both. It looks very similar in my opinion with only some
small differences.  I think it is reasonable to keep the gamma model.  Is it not
possible to compare the AIC's? When I try to find the AIC for log normal model
I am unable to.
```{r}
library(car)
resids_log_normal <- residuals(log_normal_model)
resids_gamma <- residuals(dash_and_hurdles_with_dq_two_effect_gamma_log)
qqPlot(resids_log_normal)
qqPlot(resids_gamma)
```

>>>>

Here is the qq plot for both. It looks very similar in my opinion with only some
small differences.  I think it is reasonable to keep the gamma model.  Is it not
possible to compare the AIC's? When I try to find the AIC for log normal model
I am unable to.
```{r}
library(car)
resids_log_normal <- residuals(log_normal_model)
resids_gamma <- residuals(dash_and_hurdles_with_dq_two_effect_gamma_log)
qqPlot(resids_log_normal)
qqPlot(resids_gamma)
```
```{r}
dotplot(ranef(dash_and_hurdles_with_dq_two_effect_gamma_log, condVar = TRUE))
```
```{r}
dotplot(ranef(log_normal_model, condVar = TRUE))
```
